Exact Asymptotics for Causal Mediation Analysis

### 2024-05-29 notes/William Analysis.Rmd
Define mediation effects in write-up

set.seed(1)

@@

library(lme4)     # For fitting GLMMs using glmer()
library(MASS)     # For simulating multivariate normals using mvrnorm()
library(merDeriv) # For computing the full information matrix from models fit using lme4

# Fewer large sample sizes
all_Ns = c(100, 200, 500, 1000, 2000)

@@

@@

@@

      ## Fixed-effects
      x_pred = 0
      W_pred = c(1,1,1)

@@

@@

# Combine into a table
results = data.frame(Empirical = emp_SEs, 
                     Mean = mean_delta_SEs, Median = median_delta_SEs,
                     "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
                     "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)
# results = data.frame(n = all_Ns, Empirical = emp_SEs, 
#                      Mean = mean_delta_SEs, Median = median_delta_SEs,
#                      "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
#                      "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)

@@

>>>>

# set.seed(1)
set.seed(12345)

@@

library(lme4)     # For fitting GLMMs using glmer()
library(MASS)     # For simulating multivariate normals using mvrnorm()
library(merDeriv) # For computing the full information matrix from models fit using lme4
library(tictoc)

# Fewer large sample sizes
# all_Ns = c(100, 200, 500, 1000, 2000)
# all_Ns = c(200, 500, 1000, 2000)
all_Ns = c(200, 500, 1000)

@@

# Random effects
sigma_a_0 = 0.2
sigma_a_1 = 0.2 * abs(a_1)
cor_a0_a1 = 0.2
cov_a0_a1 = sigma_a_0 * sigma_a_1 * cor_a0_a1
theta = c(sigma_a_0, sigma_a_1, cor_a0_a1)
Sigma_a = matrix(c(sigma_a_0^2, cov_a0_a1, cov_a0_a1, sigma_a_1^2), nrow = 2, ncol = 2)

sigma_b_0 = 0.2 * abs(b_0)
sigma_b_1 = 0.2 * abs(b_1)
cor_b0_b1 = 0.2
cov_b0_b1 = sigma_b_0 * sigma_b_1 * cor_b0_b1
gamma = c(sigma_b_0, sigma_b_1, cor_b0_b1)
Sigma_b = matrix(c(sigma_b_0^2, cov_b0_b1, cov_b0_b1, sigma_b_1^2), nrow = 2, ncol = 2)

@@

set.seed(2222)

@@

      ## Fixed-effects

@@

# Save output
# save(all_a_hats, all_theta_hats, all_b_hats, all_gamma_hats, all_M_covs, all_Y_covs, all_med_hats, all_med_SEs, file = "William-Analysis_cache/MC-bin-bin-mix.RData")
# load("William-Analysis_cache/MC-bin-bin-mix.RData")
```

@@

# Combine into a table
# results = data.frame(Empirical = emp_SEs,
#                      Mean = mean_delta_SEs, Median = median_delta_SEs,
#                      "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
#                      "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)
results = data.frame(n = all_Ns, Empirical = emp_SEs,
                     Mean = mean_delta_SEs, Median = median_delta_SEs,
                     "Percent_Err_Mean" = 100*(mean_delta_SEs - emp_SEs)/emp_SEs,
                     "Percent_Err_Median" = 100*(median_delta_SEs - emp_SEs)/emp_SEs)

@@

```{r}
load("../data/Exact_Asymptotics/Bin-Bin-Mix_Results.RData")

true_med = Phi_of_xi(a, theta, b, gamma, x_pred, W_pred)

load("William-Analysis_cache/latex/unnamed-chunk-37_44bd8d1152289e689fbff9185d17042c.RData", ex <- new.env())
ls.str(ex)
```

Investigate normality of estimators
```{r}
library(ggplot2)
library(magrittr)

med_hats_to_plot = unlist(data_med_hats)
Ns_to_plot = rep(all_Ns, times = sapply(data_med_hats, length))
data_med_hat_to_plot = data.frame(med_hat = med_hats_to_plot, N = Ns_to_plot)

data_med_hat_to_plot_OLD = data_med_hat_to_plot
data_med_hat_to_plot %<>% dplyr::filter(med_hat < 4)

ggplot(data_med_hat_to_plot, aes(x = med_hat)) +
  # geom_histogram(bins = 30) +
  geom_density() +
  facet_wrap(~N, scales = "free") +
  theme_minimal()

# QQ plot for each sample size
ggplot(data_med_hat_to_plot, aes(sample = med_hat)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~N, scales = "free") +
  theme_minimal()

# Test normality in each sample size
all_norm_p_vals = c()
for(n in all_Ns){
  p_val = shapiro.test(data_med_hat_to_plot$med_hat[data_med_hat_to_plot$N == n])$p.value
  all_norm_p_vals = c(all_norm_p_vals, p_val)
}
all_norm_p_vals
```
